\Large \bf 6.824 Final Project

### 2014-05-12 writeup/paper.tex
Added optimization

\subsection{Paxos Optimizations}

>>>>

\subsection{Paxos Optimizations}
In order to improve the performance of Paxos, we implemented the Multi-Paxos leader selection optimization. This optimization solved the dueling leaders problem, preventing us from hanging forever in a loop between conflicting leaders, and also allowed us to reduce the number of RPC calls that were necessary to come to agreement, by allowing us to skip the Prepare phase of the Paxos protocol for a leader that was constant between instances. The main issue with the Multi-Paxos leader selection is ensuring that leadership information is propogated through the system and ensuring that we never agree as part of two separate partitions when the Prepare phase is skipped. Unfortunately, we discovered a number of implementation bugs with our default Paxos implementation, which we ended up fixing to end up with a fairly reliable Multi-Paxos optimized system that had a selected leader and skipped unnecessary prepare phases. The results were that the number of required RPCs was reduced by about 33\%, and that there were reduced bandwidth requirements due to the singular leadership. There was an issue that a single machine became the primary proposer, potentially limiting it based on disk and processor speeds, however this doesn't appear to be an issue at the anticipated use cases.
